Live Functional Programming with Typed Holes

### 2018-04-15 calculus.tex
nit

\matt{We could (should?) move the next paragraph to the appendix, 
before/after the proofs mentioned above; 
its not really adding much to the discussion above, 
but may be interesting to the very studious reader/prover; also, leaving it here also gives a cranky reviewer a nice weapon to hit us with}

>>>>

\matt{We could (should?) move the next paragraph to the appendix, 
before/after the proofs mentioned above; 
its not really adding much to the discussion above, 
but may be interesting to the very studious reader/prover; also, leaving it here also gives a lazy/cranky reviewer a nice weapon to hit us with}
